Working on the titanic dataset from kaggle:
First, we will load the data and create a datset from it.
For reading the csv values, we will load the 'readr' package and the 'dplyr' package into our environment.
```{r}
library(readr)
library(dplyr)
```
Next, we load the train data.
```{r}
train<-read_csv('C:/Users/win10/Downloads/titanic/train.csv')
head(train)
```
Next, we will drop the name attribute from our train data because it is not of any significance.
```{r}
train<-select(train, -Name)
```
And the PassengerId attribute as well
```{r}
train<-select(train, -PassengerId)
```
Now, we will look at our data again
```{r}
train<-select(train, -Ticket, -Cabin, -Embarked)
head(train)
colnames(train)
```
Now, we tranform the Sex column into integers where 0 represents male and 1 represents female.
```{r}
train$Sex_num <- ifelse(train$Sex=="male", 1, 0)
train<-select(train, -Sex)
head(train)
```

```{r}
head(train)
```
Doing the same to the test data:
```{r}
test<-read_csv('C:/Documents and Settings/win10/Downloads/titanic/test.csv')
id<-test$PassengerId
test<-select(test, -Name, -PassengerId, -Ticket, -Cabin, -Embarked, -Ticket)
test$Sex_num <- ifelse(test$Sex=="male", 1, 0)
test<-select(test, -Sex)
head(test)
```
Training our model using linear regression:
```{r}
model=glm(formula=Survived~Pclass+Age+SibSp+Parch+Fare+Sex_num, family = "binomial", data = train, )

```
Now, we predict the survived attribute in the test data
```{r}
test$Survived<-predict(model, test, type = "response")
```
Writing our predicted data into a csv file:
```{r}
test<-select(test, Survived)
test$PassengerId<-id
test$Survived<-ifelse(test$Survived>=0.5, 1, 0)
test<-select(test, PassengerId, Survived)
head(test)
plot(test)
data<-write_csv(x=test, path = 'data.csv')
```

